The reference model approach in feature selection problems \vspace{.1in}

### 2019-06-14 paper/ref_approach.tex
minor fix

The reference model approach has been used for long time also in the Bayesian framework, an example the pioneering work by \cite{paper:reference_lindley}. In the case of generalised linear models (GLMs), \cite{tran2012predictive} provide a procedure to estimate and do variable selection with the goal of prediction: the best approximating model is recovered by optimising the Kullback-Liebler divergence between the predictive distribution of the reference model and the approximating model plus an $l_{1}$ penalty on the submodel coefficients. The resulting problem is convex and thus many efficient optimisation algorithm are available. Following \cite{goutis1998model}, \cite{paper:original_proj}  instead project the posterior distribution of the reference model in each candidate model and then select the smallest one with enough explanatory power avoiding any prior elicitation for the submodels. In the special case of candidate models being GLMs from the exponential family, the optimisation problem corresponds to the task of finding the maximum likelihood estimate using the expected pointwise predictions of the reference model instead of the observed target values. Different extensions have followed \cite{paper:original_proj}, as \cite{nott2010bayesian} that add an $l_{1}$ penalty to select the best approximating model. A recent review of these methods together with some methodological improvements is given by \cite{paper:projpred}.

@@

Expression \eqref{eq:draw_by_draw} is not a easy an easy optimisation problem, indeed \textit{projpred} implements the projection in the special case of submodels in the GLMs family, where \eqref{eq:draw_by_draw} reduces to a maximum likelihood estimation problem. For further details on \textit{projpred} workflow and implementation see \cite{paper:projpred}.

@@

where $\theta_{j}^{0}=\sqrt{n-3}\,T_{F}(\rho_{j})$ is the true value, $\hat{\theta}_{j}$ is the posterior median of each parameter $\theta_{j}$ and \eqref{eq:SESE} is a sum of posterior expectations. We divide the errors by $(n-3)$ to have quantities independent from the number of statistical units. Note that the quantity SESE takes in account also the uncertainty, thus the shrinkage, of the posterior distributions, whereas the SSE measures only the bias in the point estimates. Note that any kind of point estimate could be used to compute the SSE, here we follow \cite{paper:dirichlet_laplace} using the posterior median. The results that we show later in Section \ref{shrinkage-signal} are not sensible to such a choice. We also take into account the posterior mean for the shrinkage factor ($\kappa_{j}$) for each parameter $\theta_{j}$, which for model \eqref{eq:normal_means_problem2} is defined as follows:

@@

@@

\hypertarget{complete-selection}{%
\subsubsection{Complete selection analysis}\label{complete-selection}}
As complete selection procedures we consider the control of the local false discovery rate \citep{paper:efron, efron2012large}, the empirical Bayes median \citep{johnstone2004needles} and the selection by posterior credible intervals. 
\\
The control of the local false discovery rate is applied through the R-package \textit{locfdr}. It consists in testing the z-values $\{z_{j}\}_{j=1}^{p}$ to belong to the theoretical null distribution $f_{0}$ (the null hypothesis, meaning no relevance) against the alternative hypothesis distribution $f_{1}$. In our case $f_{0}$ correspond to the standard normal distribution (see expression \eqref{eq:normal_means_problem2}). The quantity of interest is the local false discovery rate (loc.fdr) defined as:
\
\begin{equation}
loc.fdr(z)=P(H_{0}|z)=\frac{f_{0}(z)\pi_{0}}{f(z)}
\end{equation}
where $\pi_{0}$ is the prior probability of the null hypothesis and $f(z)=\pi_{0}f_{0}(z)+(1-\pi_{0})f_{1}(z)$ is the marginal distribution of the z-values. The latter is estimated using splines with 7 degrees of freedom and we select features with local false discovery rate under the value 0.2. Such a value is commonly suggested only because it corresponds to a Bayes factor large than 36 (assuming $p_{0}\geq0.9$), other values can be considered and in our experience do not affect the results of the comparison. We use the default setting to estimate $p_{0}$ from the data provided by the package.
\\
The empirical Bayes median procedure is given by the R-package \textit{EbayesThresh} and consists in fitting a Bayesian model with a prior composed by a mixture of a delta in zero and a heavy-tailed distribution. We use, as suggested, a Laplace distribution resulting in a thresholding property, i.e. there exists a threshold value such that all the data under that threshold have posterior median equal to zero. Therefore the selection is done including those parameters whose posterior median is different from zero. The hyperparameter of the Laplace distribution and the mixing weight of the prior are estimated by marginal maximum likelihood. 
\\
The selection by posterior credible intervals is done using the regularised horseshoe prior and selecting those features who do not include zero in the interval between the 0.05 and the 0.95 quantiles.

>>>>

The reference model approach has been used for long time also in the Bayesian framework, an example the pioneering work by \cite{paper:reference_lindley}. Following \cite{goutis1998model}, \cite{paper:original_proj} project the posterior distribution of the reference model in each candidate model by minimisation of the Kullback-Liebler divergence, and then select the smallest one with enough explanatory power avoiding any prior elicitation for the submodels. In the special case of candidate models being GLMs from the exponential family, the optimisation problem corresponds to the task of finding the maximum likelihood estimate using the expected pointwise predictions of the reference model instead of the observed target values. Different extensions have followed \cite{paper:original_proj}, as \cite{nott2010bayesian} that add an $l_{1}$ penalty to select the best approximating model and \cite{tran2012predictive}, who select the best approximating model by optimising the Kullback-Liebler divergence between the predictive distribution of the reference model and the approximating model plus an $l_{1}$ penalty on the submodel coefficients. A recent review of these methods together with some methodological improvements, as clustered projection and selection by comparison of a predictive performance utility, is given by \cite{paper:projpred}.

@@

Expression \eqref{eq:draw_by_draw} is not an easy optimisation problem, but in the special case of submodels in the GLMs family, \eqref{eq:draw_by_draw} reduces to a maximum likelihood estimation problem, which can be easily optimised (e.g. using iteratively reweighted least squares alogirthm, IRLS). For further details on \textit{projpred} workflow and implementation see \cite{paper:projpred}.

@@

where $\theta_{j}^{0}=\sqrt{n-3}\,T_{F}(\rho_{j})$ is the true value, $\hat{\theta}_{j}$ is the posterior median of each parameter $\theta_{j}$ and \eqref{eq:SESE} is a sum of posterior expectations. We divide the errors by $(n-3)$ to have quantities independent from the number of statistical units. Note that the quantity SESE takes in account also the uncertainty, thus the shrinkage, of the posterior distributions, whereas the SSE measures only the bias in the point estimates. Note also that any kind of point estimate could be used to compute the SSE, here we follow \cite{paper:dirichlet_laplace} using the posterior median. The results that we show later in Section \ref{shrinkage-signal} are not sensible to such a choice. We also take into account the posterior mean for the shrinkage factor ($\kappa_{j}$) for each parameter $\theta_{j}$, which for model \eqref{eq:normal_means_problem2} with a hierarchical shrinkage prior of the type:
Z_{j}|&\theta_{j}\overset{ind}{\sim}N(\theta_{j},1) \qquad j=1,..,p \\
&\theta_{j}|\tau,\nu_{j}\overset{ind}{\sim}N(0,\nu_{j}^{2}\tau^{2})
is defined as:
\kappa_{j}=\frac{1}{1+\tau^{2}\nu_{j}^{2}}

@@

and, thus, in our case it becomes:

@@

\hypertarget{complete-selection}{%
\subsubsection{Complete selection analysis}\label{complete-selection}}
As complete selection procedures we consider the control of the local false discovery rate \citep{paper:efron, efron2012large}, the empirical Bayes median \citep{johnstone2004needles} and the selection by posterior credible intervals. 
\\
The control of the local false discovery rate is applied through the R-package \textit{locfdr}. It consists in testing the z-values $\{z_{j}\}_{j=1}^{p}$ to belong to the theoretical null distribution $f_{0}$ (the null hypothesis, meaning no relevance) against the alternative hypothesis distribution $f_{1}$. In our case $f_{0}$ correspond to the standard normal distribution (see expression \eqref{eq:normal_means_problem2}). The quantity of interest is the local false discovery rate (loc.fdr) defined as:
\
\begin{equation}
loc.fdr(z)=P(H_{0}|z)=\frac{f_{0}(z)\pi_{0}}{f(z)}
\end{equation}
where $\pi_{0}$ is the prior probability of the null hypothesis and $f(z)=\pi_{0}f_{0}(z)+(1-\pi_{0})f_{1}(z)$ is the marginal distribution of the z-values. The latter is estimated using splines with 7 degrees of freedom and we select features with local false discovery rate under the value 0.2. Such a value is commonly suggested only because it corresponds to a Bayes factor large than 36 (assuming $\pi_{0}\geq0.9$), other values can be considered and in our experience do not affect the results of the comparison. We use the default setting to estimate $\pi_{0}$ from the data provided by the package.
\\
The empirical Bayes median procedure is given by the R-package \textit{EbayesThresh} and consists in fitting a Bayesian model with a prior composed by a mixture of a delta in zero and a heavy-tailed distribution. We use, as suggested, a Laplace distribution resulting in a thresholding property, i.e. there exists a threshold value such that all the data under that threshold have posterior median equal to zero. Therefore the selection is done including those parameters whose posterior median is different from zero. The hyperparameter of the Laplace distribution and the mixing weight of the prior are estimated by marginal maximum likelihood. 
\\
The selection by posterior credible intervals is done using the regularised horseshoe prior and selecting those features who do not include zero in the interval between the 0.05 and the 0.95 quantiles.
